---
title: "Machine Learning Final Assignment"
author: "Arturo Garcia"
date: "13/6/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(caret)
library(parallel)
library(doParallel)
library(dplyr)
library(readr)
```


```{r, cache = TRUE}
train <- read_csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv")
test <- read_csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv")
```


```{r}
number_missings<- sapply(train[,], function(x) sum(is.na(x)))
sum(complete.cases(train))

complete_case <-complete.cases(train)
(table<-xtabs(~complete_case+train$classe))
summary(table)
```

```{r}
final <- 
  train[, number_missings == 0] %>% 
  select(-c(1, 3, 4, 5, 6)) %>% 
  sample_n(1000, FALSE)
```

finaltest <- 
  test[, number_missings == 0] %>% 
  select(-c(1, 3, 4, 5, 6))

```



```{r}
set.seed(123)
inTrain = createDataPartition(y=final$classe, p = 0.6,list=FALSE)
training = final[inTrain,]
testing = final[-inTrain,]
```

```{r}
cluster <- makeCluster(detectCores()) # convention to leave 1 core for OS
registerDoParallel(cluster)
```


```{r}
ctrl <- trainControl(method="repeatedcv", number=10, repeats=5)
system.time(model <- train(classe ~ ., data=training, method="rf", trControl = ctrl))
modelError <- confusionMatrix(predict(model, newdata=testing), testing$classe)
modelError
```

```{r}
stopCluster(cluster)
registerDoSEQ() 
```

